Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-09 manuscript/manuscript.tex
editing Ne section

To help help reconcile our measure of linked selection, $G(t)$, with familiar
reductions in $N_e$, or, equivalently neutral diversity, we develop some rough
approximations here. First, we introduce some convenient notation. Let $V_{T} =
\var(p_t - p_0)$ be the total observed variation in allele frequency, $C_{LS} =
\sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)$ be the
contribution of all pairwise temporal covariances (observable), $V_D$ be the
unobservable drift-only variance in allele frequency, and $V_{LS} =
\sum_{i=0}^{t-1} \var(\Delta_{LS} p_i$ which is the (unobservable) effect
linked selection has on the variances in allele frequency change.

@@

Under a Wright--Fisher population,

>>>>

To help help reconcile our measure of linked selection, $G(t)$, with familiar
reductions  \gc{in neutral diversity, as parameterized by} $N_e$, we develop some rough
approximations here. First, we introduce some convenient notation. Let $V_{T} =
\var(p_t - p_0)$ be the total observed variation in allele frequency, $C_{LS} =
\sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)$ be the
contribution of all pairwise temporal covariances (observable), $V_D$ be the
unobservable drift-only variance in allele frequency, and $V_{LS} =
\sum_{i=0}^{t-1} \var(\Delta_{LS} p_i$ which is the (unobservable) effect
linked selection has on the variances in allele frequency change.

@@

\gc{In a neutral} Wright--Fisher population,
